Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-19 chi2012.tex
Minor fixes in background section.

In this section, we motivate our work using three fields: PIM, data integration, and end-user mashups and toolkits.  Our primary motivation stems from field studies in PIM, where consolidating and working with data from multiple sources has remained a challenge for over a decade. Enabling PIM tools to supporting ad-hoc data integration has remained difficult because of the complex, theoretically difficult nature of data heterogeneity; specifically, reconciling the differences that arise among representations when data is created by different people, at different times, for different purposes. As described by Alon Halvey:

>>>>

In this section, we motivate our work using three fields: PIM, data integration, and end-user mashups and toolkits.  Our primary motivation stems from field studies in PIM, where consolidating and working with data from multiple sources has remained a challenge for over a decade. Enabling PIM tools to support ad-hoc data integration has remained difficult because of the complex, theoretically difficult nature of data heterogeneity; specifically, reconciling the differences that arise among representations when data is created by different people, at different times, for different purposes. As described by Alon Halvey:
